\documentclass[11pt]{article}

%\usepackage[american]{babel}
%\usepackage{times}
%\usepackage{palatino}           % rm font
%\usepackage{helvet}             % sf font
%\usepackage{courier}            % tt font

\usepackage[hyphens]{url}
\usepackage[final,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=blue]{hyperref}
\usepackage{verbatim}

% \usepackage{hyperref}
%%MO: NSF requires 2.5cm margins and at least 10pt

% vertical spacing,
\voffset0in
\topmargin0in
\headheight0in
\headsep0in
\textheight9.0in
\footskip.4in

% horizontal spacing
\hoffset0in
\oddsidemargin0in
\evensidemargin0in
% \columnsep.1in (doesn't matter for NSF)
\marginparsep0in
\textwidth6.5in

\parindent 0in

% avoid widow lines
\widowpenalty=1000

\renewcommand{\baselinestretch}{1.0}

\newcommand{\hangpara}{
 \setlength{\parindent}{0in} % don't indent new paragraphs
 \hangindent=0.42in % indent all subsequent lines
}


\begin{document}
\pagestyle{empty}


\begin{center}
{\bf CURRICULM VITAE\\Steven Moran}\\

\vskip 12pt

\begin{tabular}{ll}
% \begin{tabular}{p{6cm}p{10cm}}
% Institut f{\"u}r Vergleichende Sprachwissenschaft & & \\
% Plattenstrasse 54, Raum 206 & & steven.moran at uzh.ch\\
% Universit{\"a}t Zurich & & \url{http://www.spw.uzh.ch/moran.html}\\
% 8032 Zurich, Schweiz & & +41 44 63 40221\\
%
% Department of Comparative Linguistics & & \href{mailto:steven.moran@uzh.ch}{steven.moran@uzh.ch} \\
% University of Zurich & & +41 44 63 40221 \\
% Plattenstrasse 54, Room 206 & & \small\url{orcid.org/0000-0002-3969-6549} \\
% 8032 Zurich, Switzerland & & \\

% Language and Space Lab & & \href{mailto:steven.moran@uzh.ch}{steven.moran@uzh.ch} \\
% University of Zurich & & \small\url{orcid.org/0000-0002-3969-6549} \\
% Freiestrasse 16 & & \\
% 8032 Zurich, Switzerland & & \\

Institute of Biology   & steven.moran at unine.ch \\
University of Neuchâtel & +41 32 718 24 30 \\
Rue Emile-Argand 11, G B35 & \href{https://www.unine.ch/evolang/home/team/steven-moran.html}{unine.ch/evolang/home/team/steven-moran.html} \\
2000 Neuchâtel & \href{https://orcid.org/0000-0002-3969-6549}{orcid.org/0000-0002-3969-6549} \\
Switzerland & \\
% & & \\
% \small\url{orcid.org/0000-0002-3969-6549}
% \small\url{https://www.unine.ch/evolang/home/team/steven-moran.html} & & \\
% \small\url{https://scholar.google.com/citations?user=PpTOh08AAAAJ&hl=en} & & \\
% \small\url{https://github.com/bambooforest/} & & \\
% \small\url{https://www.linkedin.com/in/steven-moran-b59b3b3/} & & \\
% \small\url{https://twitter.com/stivits} & & \
\end{tabular}
\end{center}

\vskip 12pt
\begin{flushleft}
{\bf EMPLOYMENT}
\end{flushleft}
\begin{tabular}{lp{5.5in}}

\bf 2020--2025 & {\bf University of Neuchâtel} \\
& Assistant professor, Institute of Biology \\
& Director of the Language Evolution Lab \\
& Principle investigator of Swiss National Science Foundation project: EVOPHON \\
% PI of Swiss National Science Foundation funded project: EVOPHON.\\
% Laboratoire d'évolution du langage

\bf 2012--2020 & {\bf University of Zurich} \\
% & Postdoctoral researcher Language and Space Lab (2020). Postdoctoral researcher and instructor in the Department of Comparative Linguistics (2012--2019). Postdoctoral researcher and technical project manager for the ACQDIV project (2014--2019).  \\

& Postdoc in Language and Space Lab (2020) \\
& Postdoc and instructor in Department of Comparative Linguistics (2012--2019) \\
& Postdoc and technical project manager in ERC ACQDIV (2014--2019) \\


% \bf 2013--2014 & {\bf Philipps Universit{\"a}t Marburg} \\
\bf 2013--2014 & {\bf University of Marburg} \\
% & Postdoctoral researcher and programmer in the Quantitative Language Comparison Research Unit in the Forschungszentrum Deutscher Sprachatlas. \\
& Posdoc in ERC QuantHistLing, Forschungszentrum Deutscher Sprachatlas \\

% \bf 2010--2013 & {\bf Ludwig-Maximilians-Universit{\"a}t M{\"u}nchen} \\
\bf 2010--2013 & {\bf University of Munich} \\
% & Researcher and programmer in the Quantitative Language Comparison Research Unit. \\
& Research assistant in ERC QuantHistLing \\

\bf 2005--2010 & {\bf University of Washington} \\
% & Technical project manager for Phonetics Information Base and Lexicon (2009; UW Royalty Research Fund); Research assistant on Implementing the GOLD Community of Practice: Laying the Foundations for a Linguistics Cyberinfrastructure (2008; National Science Foundation (NSF) Grant BCS--0720670); User interface designer for UW Information Technology (2007--2008); Web programmer and Computer Assisted Language Learning specialist for UW Language Learning Center (2005--2007) \\
& Instructor in Department of Linguistics (2007--2010) \\
& Technical project manager in UW RRF PHOIBLE (2009) \\
& Research assistant in NSF GOLD (2008) \\
& Research assistant at UW Information Technology (2007--2008) \\ % UX programmer
& Research assistant at UW Language Learning Center (2005--2007) \\

\bf 2001--2005 & {\bf Eastern Michigan University} \\ 
& Technical project manager in NSF E-MELD (2003--2005) \\
& Research assistant and editor at Linguist List (2001--2003) \\
\end{tabular}

\vskip 12pt
\begin{flushleft}
{\bf EDUCATION}
\end{flushleft}
\begin{tabular}{ll}
\bf 2012 & University of Washington, Seattle \textbf{Ph.D.\ in Linguistics} \\
& Dissertation: \textit{Phonetics Information Base and Lexicon} \href{https://digital.lib.washington.edu/researchworks/handle/1773/22452}{[pdf]} \\
& Commitee: Emily Bender (Co-chair), Richard Wright (Co-chair), Scott Farrar, Sharon Hargus \\
\bf 2006 & Eastern Michigan University, \textbf{M.A.\ in Linguistics}  \\
& Thesis: {\it A Grammatical Sketch of Western Sisaala} \href{http://commons.emich.edu/theses/73/}{[pdf]}\\
& Commitee: Verònica Grondona (Chair), Edward Garrett \\
\bf 2006 & Eastern Michigan University, \textbf{M.A.\ Certificate in Language Technology}  \\
\bf 2001 & Eastern Michigan University, \textbf{B.A.\ with honors in German, Linguistics and TESOL}  \\
\bf 2000 & Sprachaufenthalt, Volkshochschule, Karlsruhe, Germany \\
\bf 1999 & Austauschprogramm Deutsch in Graz, Graz, Austria \\
\end{tabular}

\clearpage
% \vskip 12pt
\begin{flushleft}
{\bf JOURNAL PUBLICATIONS}
\end{flushleft}

% \vskip 6pt

\hangpara
{\bf 2021}\hspace{1ex}Levshina, Natalia and Steven Moran. Efficiency in human languages: corpus evidence for universal principles. \textit{Linguistics Vanguard}, 7, S3. \url{https://doi.org/10.1515/lingvan-2020-0081}.

\hangpara
\vskip 6pt
{\bf 2021}\hspace{1ex}Moran, Steven, Nicholas A. Lester and Eitan Grossman. Inferring recent evolutionary changes in speech sounds. \textit{Philosophical Transactions of the Royal Society B: Biological Sciences}, 376: 20200198. \url{https://doi.org/10.1098/rstb.2020.0198}.

\hangpara
\vskip 6pt
{\bf 2021}\hspace{1ex}Urban, Matthias and Steven Moran. Altitude and the distributional typology of language structure: ejectives and beyond. \textit{PLoS ONE}, 16(2): e0245522. \url{https://doi.org/10.1371/journal.pone.0245522}.

\hangpara
\vskip 6pt
{\bf 2020}\hspace{1ex}Moran, Steven, Eitan Grossman and Annemarie Verkerk. Investigating diachronic trends in phonological inventories using BDPROTO. \textit{Language Resource and Evaluation}, 55, 79--103. \url{https://doi.org/10.1007/s10579-019-09483-3}.

\hangpara
\vskip 6pt
{\bf 2019}\hspace{1ex}Blasi, Dami{\'a}n E.$^*$, Steven Moran$^*$, Scott R. Moisik, Paul Widmer, Dan Dediu and Balthasar Bickel. Human sound systems are shaped by post-Neolithic changes in bite configuration. \textit{Science}, 363, 6432. \url{http://dx.doi.org/10.1126/science.aav3218}. $^*$Shared first authorship. % \url{https://science.sciencemag.org/content/363/6432/eaav3218}. 

\hangpara
\vskip 6pt
{\bf 2018}\hspace{1ex}Moran, Steven, Dami{\'a}n E. Blasi, Robert Schikowski, Aylin C. K{\"u}ntay, Barbara Pfeiler, Shanley Allen and Sabine Stoll. A universal cue for grammatical categories in the input to children: frequent frames. \textit{Cognition}, 175, 131--140. \url{https://doi.org/10.1016/j.cognition.2018.02.005}. % \url{https://www.sciencedirect.com/science/article/pii/S0010027718300362}.

\hangpara
\vskip 6pt
{\bf 2016}\hspace{1ex}Moran, Steven. Commentary: Issues of time, tone, roots and replicability. \textit{Journal of Language Evolution}, 1(1), 73–-76. \url{https://doi.org/10.1093/jole/lzv011}

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}Stoll, Sabine, Taras Zakharko, Steven Moran, Robert Schikowski and Balthasar Bickel. Syntactic mixing across generations in an environment of community-wide bilingualism. \textit{Frontiers in Psychology}. Special Topic: Acquisition in Contact Research, Shannessy Carmel (ed). \url{https://doi.org/10.3389/fpsyg.2015.00082}. %\url{http://journal.frontiersin.org/Journal/10.3389/fpsyg.2015.00082/abstract}

\hangpara
\vskip 6pt
{\bf 2015}\hspace{1ex}McCrae, John, Steven Moran, Sebastian Hellmann and Martin Brümmer. Multilingual Linked Open Data. \textit{Semantic Web}, 6(4), 315--317. \url{https://doi.org/10.3233/SW-150178}. \url{http://www.semantic-web-journal.net/system/files/swj1042\_0.pdf}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Moran, Steven and Jelena Proki{\'c}. Investigating the Relatedness of the Endangered Dogon Languages. \textit{Literary And Linguistic Computing}, 28(4) 676--691. Oxford University Press. \url{https://doi.org/10.1093/llc/fqt061}

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}Moran, Steven, Daniel McCloy and Richard Wright. Revisiting population size vs phoneme inventory size. {\it Language}, 88(4): 877--893. \url{https://doi.org/10.1353/lan.2012.0087}. % \url{http://muse.jhu.edu/journals/language/v088/88.4.moran.html}

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}Cysouw, Michael, Dan Dediu and Steven Moran. Comment on ``Phonemic Diversity Supports a Serial Founder Effect Model of Language Expansion from Africa''. \textit{Science}, 335(6069):657. \url{https://doi.org/10.1126/science.1208841}.

% \url{http://www.sciencemag.org/content/335/6069/657.2.full}
% 10.1126/science.1208841.
% 10 February 2012. 

\clearpage
\vskip 20pt
\begin{flushleft}
{\bf BOOK}
\end{flushleft}

\hangpara
{\bf 2018}\hspace{1ex}Moran, Steven and Michael Cysouw. {\it The Unicode Cookbook for Linguists: Managing writing systems using orthography profiles}. Translation and Multilingual Natural Language Processing series in Language Science Press. \url{https://doi.org/10.5281/zenodo.1296780}. \url{http://langsci-press.org/catalog/book/176}.


\vskip 20pt
\begin{flushleft}
{\bf BOOK CHAPTERS}
\end{flushleft}

\hangpara{\bf In press.}\hspace{1ex}Moran, Steven. Managing Phonological Inventory Data in the Development of PHOIBLE. In Andrea L. Berez-Kroeker, Bradley McDonnell, and Eve Koller (eds), \textit{The Open Handbook of Linguistic Data Management: Open Handbooks in Linguistics}. MIT Press.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Moran, Steven and Christian Chiarcos. Linguistic Linked Open Data and Under-Resourced Languages: From Collection to Application. In Antonio Pareja-Lora, María Blume, Barbara C. Lust, and Christian Chiarcos (eds), \textit{Development of Linguistic Linked Open Data Resources for Collaborative Data-Intensive Research in the Language Sciences}. MIT Press. \url{https://doi.org/10.7551/mitpress/10990.001.0001}.

% \url{https://mitpress.mit.edu/books/development-linguistic-linked-open-data-resources-collaborative-data-intensive-research-language}

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Benitez-Burraco, Antonio and Steven Moran. The Adaptive Value of Languages: Non-Linguistic Causes of Language Diversity. In Benitez-Burraco, Antonio and Steven Moran (eds), \textit{The Adaptive Value of Languages: Non-Linguistic Causes of Language Diversity}. Frontiers in Psychology. \url{https://doi.org/10.3389/fpsyg.2018.01827}.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Moran, Steven and Dami{\'a}n Blasi. Cross-linguistic comparison of complexity measures in phonological systems. In Frederick J. Newmeyer and Laurel Preston (eds), {\it Measuring Grammatical Complexity}. Oxford University Press. 

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Proki{\'c}, Jelena and Steven Moran. Black box approaches to genealogical classification and their shortcomings. In {\it Comparing Approaches to Measuring Linguistic Differences}, Lars Borin and Anju Saxena (eds), 429--446. Berlin, Boston: De Gruyter Mouton. \url{https://doi.org/10.1515/9783110305258.429}

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Chiarcos, Christian, Steven Moran, Pablo N. Mendes, Sebastian Nordhoff, Richard Littauer. Building a Linked Open Data Cloud of Linguistic Resources: Motivations and Developments. In Iryna Gurevych and Jungi Kim (eds), {\it The People's Web Meets NLP: Collaboratively Constructed Language Resources}. Springer, Berlin, Heidelberg. \url{https://doi.org/10.1007/978-3-642-35085-6_12}.

% \url{https://link.springer.com/chapter/10.1007/978-3-642-35085-6_12} % 315--348
% http://www.ukp.tu-darmstadt.de/scientific-community/edited-book-the-peoples-web-meets-nlp

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}Moran, Steven. Using Linked Data to Create a Typological Knowledge Base. In {\it Linked Data in Linguistics: Representing and Connecting Language Data and Language Metadata}, Christian Chiarcos, Sebastian Nordhoff and Sebastian Hellmann (eds). Springer, Heidelberg. \url{https://doi.org/10.1007/978-3-642-28249-2_13}. \url{http://svn.aksw.org/papers/2012/LDL/ldl2012_proceedings/public/moran.pdf}.

\vskip 6pt
\hangpara
{\bf 2011}\hspace{1ex}Moran, Steven. An Ontology for Accessing Transcription Systems. In {\it Language Resources \& Evaluation: Special Issue on African Language Technology}, Guy De Pauw, Laurette Pretorius, Gilles-Maurice de Schryver and Lori Levin (eds). \url{https://doi.org/10.1007/s10579-011-9158-8}. \url{https://link.springer.com/article/10.1007/s10579-011-9158-8}.% 345--360 - Volume 45, Issue 3 Heidelberg

\vskip 6pt
\hangpara
{\bf 2010}\hspace{1ex}Boynton, Jessica, Steven Moran, Helen Aristar-Dry and Anthony Aristar. Using the E-MELD School of Best Practices to Create Lasting Digital Documentation. In {\it Language Documentation: Practice and Values}, Lenore A. Grenoble and N. Louanna Furbee (eds), 133--146. John Benjamins. \url{https://doi.org/10.1075/z.158.14boy}.


\vskip 20pt
\begin{flushleft}
{\bf CONFERENCE \& WORKSHOP PROCEEDINGS (PEER-REVIEWED)}
\end{flushleft}

\hangpara
{\bf 2020}\hspace{1ex}Lester, Nicholas A., Balthasar Bickel, Steven Moran and Sabine Stoll. Speech Rates Differentiate Nouns and Verbs in Child-Surrounding and Child-Produced Speech: Evidence from Chintang. In M. M. Brown \& A. Kohut (Eds.), Proceedings 44th Annual Boston University Conference on Language Development (BUCLD), 280--293. Somerville, MA: Cascadilla Press. \url{http://www.lingref.com/bucld/44/BUCLD44-23.pdf}.

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Grossman, Eitan, Elad Eisan, Dmitry Nikolaev and Steven Moran. SegBo: A Database of Borrowed Sounds in the World's Languages. In Proceedings of the Twelfth International Conference on Language Resources and Evaluation (LREC 2020). \url{http://www.lrec-conf.org/proceedings/lrec2020/pdf/2020.lrec-1.654.pdf}. % May 13--15, Marseille, France. 

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Jancso, Anna*, Steven Moran*  and Sabine Stoll. The ACQDIV Corpus Database and Aggregation Pipeline. In Proceedings of the Twelfth International Conference on Language Resources and Evaluation (LREC 2020). *Shared first authorship. \url{http://www.lrec-conf.org/proceedings/lrec2020/pdf/2020.lrec-1.20.pdf}. % May 13--15, Marseille, France. 

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Grossman, Eitan, Elad Eisan, Dmitry Nikolaev and Steven Moran. Revisiting the Uniformitarian Hypothesis: Can we detect recent changes in the typological frequencies of speech sounds?  In Proceedings of the 13th International Conference on the Evolution of Language (EVOLANG 2020). \url{https://brussels.evolang.org/proceedings/papers/EvoLang13_paper_182.pdf} % April 14--17, Brussels, Belgium. 

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Loukatou, Georgia R., Steven Moran, Dami{\'a}n E. Blasi, Sabine Stoll and Alejandrina Cristia. Is word segmentation child's play in all languages? In Proceedings of the 57th Annual Meeting of the Association for Computational Linguistics, 3931--3937. July 28 -- August 2, Florence, Italy.  \url{https://www.aclweb.org/anthology/P19-1383}.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Moran, Steven, Nicholas A. Lester, Heath Gordon, Aylin Küntay, Barbara Pfeiler, Shanley Allen and Sabine Stoll. Variation Sets in Maximally Diverse Languages. In Proceedings 43rd annual Boston University Conference on Language Development (BUCLD). November 2--4, Boston, USA. Cascadilla Press. \url{http://www.lingref.com/bucld/43/BUCLD43-34.pdf}

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Moran, Steven, Danica Pajovi{\'c} and Sabine Stoll. Cross-linguistically Small World Networks are Ubiquitous in Child-directed Speech. In Proceedings of the Eleventh International Conference on Language Resources and Evaluation (LREC 2018), 4100-4105. May 7--12, Miyazaki, Japan.  \url{http://www.lrec-conf.org/proceedings/lrec2018/pdf/887.pdf}

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Marsico, Egidio, Sebastien Flavier, Annemarie Verkerk and Steven Moran. BDPROTO: A Database of Phonological Inventories from Ancient and Reconstructed Languages. In Proceedings of the Eleventh International Conference on Language Resources and Evaluation (LREC 2018), 1654--1658. May 7--12, Miyazaki, Japan. \url{http://www.lrec-conf.org/proceedings/lrec2018/pdf/534.pdf}

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}McNew, Garland, Curdin Derungs and Steven Moran. Towards faithfully visualizing global linguistic diversity. In Proceedings of the Eleventh International Conference on Language Resources and Evaluation (LREC 2018), 805--809. May 7--12, Miyazaki, Japan. \url{http://www.lrec-conf.org/proceedings/lrec2018/pdf/813.pdf}

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Moran, Steven and Annemarie Verkerk. Differential rates of change in consonant and vowel systems. In C. Cuskley and M. Flaherty and H. Little and Luke McCrohon and A. Ravignani and T. Verhoef (eds.), The Evolution of Language: Proceedings of the 12th International Conference (EVOLANGXII). April 16--19, Toru{\'n}, Poland. \url{https://doi.org/10.12775/3991-1.077}. \url{http://evolang.org/torun/proceedings/papertemplate.html?p=98}.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Moran, Steven, Robert Schikowski, Danica Pajovi{\'c}, Cazim Hysi and Sabine Stoll. The ACQDIV Database: Min(d)ing the Ambient Language. In Proceedings of the Tenth International Conference on Language Resources and Evaluation (LREC 2016), 4423--4429. May 23--28, Portoro{\v z}, Slovenia. \url{http://www.lrec-conf.org/proceedings/lrec2016/pdf/1198\_Paper.pdf}.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}McCrae, John Philip, Christian Chiarcos, Francis Bond, Philipp Cimiano, Thierry Declerck, Gerard de Melo, Jorge Gracia, Sebastian Hellmann, Bettina Klimek, Steven Moran, Petya Osenova, Antonio Pareja-Lora and Jonathan Pool. The Open Linguistics Working Group: Developing the Linguistic Linked Open Data Cloud. In Proceedings of the Tenth International Conference on Language Resources and Evaluation (LREC 2016), 2435--2441. May 23--28, Portoro{\v z}, Slovenia. \url{http://www.lrec-conf.org/proceedings/lrec2016/pdf/851\_Paper.pdf}.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Moran, Steven and Michael Cysouw. ￼Typology with Graphs and Matrices. In Proceedings of the Third Workshop on Linked Data in Linguistics, Multilingual Knowledge Resources and Natural Language Processing, 55--60. Co-located with LREC 2014. May 27, Reykjavik, Iceland. \url{http://www.lrec-conf.org/proceedings/lrec2014/workshops/LREC2014Workshop-LDL2014\%20Proceedings.pdf}.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Goldman, Jean-Philippe, Adrian Leemann, Marie-Jos{\'e} Kolly, Ingrid Hove, Ibrahim Almajai, Volker Dellwo and Steven Moran. ￼A Crowdsourcing Smartphone Application for Swiss German: Putting language documentation in the hands of the users. In Proceedings of the Ninth International Conference on Language Resources and Evaluation (LREC 14), Nicoletta Calzolari, Khalid Choukri, Thierry Declerck, Hrafn Loftsson, Bente Maegaard, Joseph Mariani, Asuncion Moreno, Jan Odijk and Stelios Piperidis (eds). May 26--31, Reykjavik, Iceland. \url{http://www.lrec-conf.org/proceedings/lrec2014/pdf/214_Paper.pdf}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Moran, Steven and Martin Brümmer. Lemon-aid: using Lemon to aid quantitative historical linguistic analysis. In Proceedings of the 2nd Workshop on Linked Data in Linguistics (LDL-2013): Representing and linking lexicons, terminologies and other language data. Christian Chiarcos, Philipp Cimiano, Thierry Declerck and John P. McCrae (eds). Association for Computational Linguistics. September, 23. Pisa, Italy. \url{http://aclweb.org/anthology/W/W13/W13-5505.pdf}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Littauer, Richard, Boris Villazon-Terrazas and Steven Moran. Linguistic Resources Enhanced with Geospatial Information. In Proceedings of the 2nd Workshop on Linked Data in Linguistics (LDL-2013): Representing and linking lexicons, terminologies and other language data. Christian Chiarcos, Philipp Cimiano, Thierry Declerck and John P. McCrae (eds). Association for Computational Linguistics. September, 23. Pisa, Italy. \url{http://aclweb.org/anthology/W/W13/W13-5508.pdf}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}List, Johann-Mattis and Steven Moran. An Open Source Toolkit for Quantitative Historical Linguistics. In {\it Proceedings of the 51st Annual Meeting of the Association for Computational Linguistics}, pg 13--18, Sofia, Bulgaria, August 4--9, 2013. \url{http://aclweb.org/anthology/P/P13/P13-4003.pdf}.

% \vskip 6pt
% \hangpara
% {\bf Frth}\hspace{1ex}Moran, Steven and Jelena Proki{\'c}. Investigating the relatedness of the endangered Dogon languages. To appear in proceedings of Digital % Humanities 2012. Hamburg, Germany.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}Chiarcos, Christian, Sebastian Hellmann, Sebastian Nordhoff, Steven Moran, Richard Littauer, Judith Eckle-Kohler, Iryna Gurevych, Silvana Hartmann, Michael Matuschek and Christian M. Meyer.  `The Open Linguistics Working Group'. In {\it Proceedings from LREC 2012}, pg 3603--3610, Istanbul, Turkey, May 23--25. \url{http://www.lrec-conf.org/proceedings/lrec2012/pdf/912_Paper.pdf}.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}Moran, Steven, Daniel McCloy and Richard Wright. `Revisiting the population vs phoneme-inventory correlation'. In {\it Extended abstracts in eLanguage from LSA 2012}. \url{http://dx.doi.org/10.3765/exabs.v0i0.601}.

\vskip 6pt
\hangpara
{\bf 2009}\hspace{1ex}Moran, Steven. An Ontology for Accessing Transcription Systems. In {\it Proceedings from the African Language Technology Workshop at the European Association for Computational Linguistics}. Athens, Greece, March 31. \url{http://www.aclweb.org/anthology/W09-0716}. % 112--120 Association for Computational Linguistics

\vskip 6pt
\hangpara
{\bf 2008}\hspace{1ex}Farrar, Scott and Steven Moran. The e-Linguistics Toolkit. In {\it Proceedings e-Humanities --- an emerging discipline: Workshop in the 4th IEEE International Conference on e-Science}. Indianapolis, Indiana. \url{http://www.zora.uzh.ch/id/eprint/84686/1/FarrarMoran2008.pdf}

\vskip 6pt
\hangpara
{\bf 2008}\hspace{1ex}Trippel, Thorsten, Michael Maxwell, Greville Corbett, Cambell Prince, Christopher Manning, Stephen Grimes and Steven Moran. Lexicon Schemas and Related Data Models: When Standards Meet Users. In {\it Proceedings of the 6th International Conference on Language Resources and Evaluation (LREC)}. Marrakech, Morocco. \url{http://www.lrec-conf.org/proceedings/lrec2008/pdf/812_paper.pdf}.

\vskip 6pt
\hangpara
{\bf 2008}\hspace{1ex}Fox, Naomi and Steven Moran. Non-traditional Dissemination of Fieldwork: From the Field to the World. In {\it Proceedings from the 20th Northwest Linguistics Conference (NWLC)}, Steven Moran, Darren S. Tanner and Michael Scanlon (eds). Seattle, Washington. \url{https://depts.washington.edu/uwwpl/vol27/uwwpl_vol27_2008.pdf}. % 109--114

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}Boynton, Jessica, Steven Moran, Anthony Aristar and Helen Aristar-Dry. E-MELD and the School of Best Practices: An Ongoing Community Effort. In {\it Proceedings from Sustainable Data from Digital Fieldwork.} Sydney University Press. \url{https://ses.library.usyd.edu.au/bitstream/2123/1296/1/9FH2006.pdf}. % 87--97

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}Moran, Steven. From Field Methods to Best Practice: A Case Study of Western Sisaala. E-MELD School of Best Practices. \url{http://emeld.org/school/case/sisaala/index.html}

\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}Moran, Steven. The E-MELD School of Best Practices in Digital Language Documentation. In {\it Proceedings from the Annual Meeting of the Chicago Linguistic Society}, 41(2), 71--80. Chicago Linguistic Society. \url{http://chicagolinguisticsociety.org/public/cls41-2-toc.pdf}.

% Rodney L. Edwards, Patrick J. Midtlyng, Colin L. Sprague, and Kjersti K. Stensrud

\vskip 6pt
\hangpara
{\bf 2004}\hspace{1ex}Ferrara, Marisa and Steven Moran. Review of DBMS for Linguistic Purposes. In {\it Proceedings from the E-MELD 2004: Conference on Linguistic Databases and Best Practices}. \url{http://emeld.org/workshop/2004/papers.html}

\clearpage

\vskip 20pt
\begin{flushleft}
{\bf EDITED VOLUMES}
\end{flushleft}

\hangpara
{\bf 2021}\hspace{1ex}Levshina, Natalia and Steven Moran (eds). Efficiency in human languages: corpus evidence for universal principles. {\it Linguistics Vanguard}, 7, 3. \url{https://www.degruyter.com/journal/key/LINGVAN/7/s3/html}.

\hangpara
\vskip 6pt
{\bf 2018}\hspace{1ex}Benitez-Burraco, Antonio and Steven Moran (eds). The Adaptive Value of Languages: Non-Linguistic Causes of Language Diversity. {\it Frontiers in Psychology}. \url{http://journal.frontiersin.org/researchtopic/5478/the-adaptive-value-of-languages-non-linguistic-causes-of-language-diversity}

\hangpara
\vskip 6pt
{\bf 2015}\hspace{1ex}Hellmann, Sebastian, Steven Moran, Martin Brümmer and John McCrae (eds). Special Issue on Multilingual Linked Open Data (MLOD). \textit{Semantic Web}, 6(4). \url{https://content.iospress.com/journals/semantic-web/6/4}.

\vskip 6pt
\hangpara
{\bf 2008}\hspace{1ex}Moran, Steven, Darren Tanner and Michael Scanlon (eds). Proceedings from the 20th Northwest Linguistics Conference (NWLC). University of Washington Working Papers in Linguistics Vol. 27. \url{http://depts.washington.edu/uwwpl/vol27/}.

\vskip 6pt
\hangpara
{\bf 2007}\hspace{1ex}Moran, Steven (ed). University of Washington Working Papers in Linguistics Vol 26. \url{http://depts.washington.edu/uwwpl/vol26/}.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}Moran, Steven (ed). University of Washington Working Papers in Linguistics Vol. 25. \url{http://depts.washington.edu/uwwpl/vol25/}.

\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}Jinguji, Dan and Steven Moran (eds). University of Washington Working Papers in Linguistics Vol. 24. \url{http://depts.washington.edu/uwwpl/vol24/}.

\vskip 6pt
\hangpara
{\bf 2001--2005}\hspace{1ex}Moran, Steven (ed). The Linguist List. ISSN: 1068--4875. 420 issues. \url{http://linguistlist.org}.


\vskip 20pt
\begin{flushleft}
{\bf RESPONSES}
\end{flushleft}

\hangpara
{\bf 2020}\hspace{1ex}Moran, Steven and Balthasar Bickel. Rejoinder to Huijbregts’s: Biting into Evolution of Language. \textit{Journal of Language Evolution}, 5(2), 184--187. \url{https://doi.org/10.1093/jole/lzaa005}.

\vskip 6pt
\hangpara
{\bf 2020} Blasi, Damián E., Steven Moran, Scott R. Moisik, Paul Widmer, Dan Dediu and Balthasar Bickel. Languages, evolution and statistics: human sound systems were shaped by changes in bite configuration. Response to Tarasov \& Uyeda (2020). \textit{bioRxiv}. \url{https://doi.org/10.1101/2020.02.27.965400}.


\vskip 20pt
\begin{flushleft}
{\bf OUTREACH}
\end{flushleft}

% Media
% Alphaman

\hangpara
{\bf 2019}\hspace{1ex}Die Ernährung verändert die Sprache. 3sat Nano TV Program. \url{https://www.3sat.de/wissen/nano/191209-sprache-nano-104.html}.

\hangpara
\vskip 6pt
{\bf 2019}\hspace{1ex}Moran, Steven and Balthasar Bickel. Softer, processed foods changed the way ancient humans spoke. \textit{The Conversation}. \url{https://theconversation.com/softer-processed-foods-changed-the-way-ancient-humans-spoke-113599}. Translated into Bahasa Indonesian by Jamiah Solehati (\url{https://theconversation.com/makanan-olahan-yang-lebih-lembut-ubah-cara-manusia-purba-berbicara-115509}).

\hangpara
\vskip 6pt {\bf 2018}\hspace{1ex}What it means to be open and community-based: The Unicode cookbook as a showcase. Interview with Sebastian Nordhoff of Language Science Press. \url{https://userblogs.fu-berlin.de/langsci-press/2018/07/11/what-it-means-to-be-open-and-community-based-the-unicode-cookbook-as-a-showcase/}.


\vskip 20pt
\begin{flushleft}
{\bf PUBLISHED DATASETS AND SOFTWARE}
\end{flushleft}

\hangpara
{\bf 2020}\hspace{1ex}Grossman, Eitan, Elad Eisen, Dmitry Nikolaev, and Steven Moran. segbo-db/segbo (Version v1.0.0) [Data set]. Zenodo. \url{https://doi.org/10.5281/zenodo.3633917}. \url{https://github.com/segbo-db/segbo}.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Moran, Steven, Anna Jancso and Sabine Stoll. ACQDIV database (public) (Version 1.0.0) [Data set]. Zenodo. \url{https://doi.org/10.5281/zenodo.3558641}.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Moran, Steven and Anna Jancso. ACQDIV database aggregation pipeline (Version 1.0.0). Zenodo. \url{https://doi.org/10.5281/zenodo.3558641}. \url{https://github.com/acqdiv/acqdiv}.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Moran, Steven and Eitan Grossman. BDPROTO 1.1 (Version 1.1) [Data set]. Zenodo. \url{https://doi.org/10.5281/zenodo.3522973}. \url{https://github.com/bdproto}.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Marsico, Egidio, Sébastien Flavier and Steven Moran. BDPROTO 1.0 (Version 1.0) [Data set]. Zenodo. \url{https://doi.org/10.5281/zenodo.3521639}. \url{https://github.com/bdproto}.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Moran, Steven and Daniel McCloy (eds). PHOIBLE 2.0. Jena: Max Planck Institute for the Science of Human History. \url{https://doi.org/10.5281/zenodo.2562766}. \url{http://phoible.org}.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}Moran, Steven and Robert Forkel. cldf/segments: segments 1.1.1 (Version v1.1.1). Zenodo. \url{https://doi.org/10.5281/zenodo.1051158}. \url{https://pypi.org/project/segments}.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Moran, Steven, Forkel, Robert and Jeffrey Heath (eds). Dogon and Bangime Linguistics. Jena: Max Planck Institute for the Science of Human History. \url{http://dogonlanguages.org}.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}Naumann, Christfried, Moran, Steven, Segerer, Guillaume and Robert Forkel (eds). Tsammalex: A lexical database on plants and animals. Leipzig: Max Planck Institute for Evolutionary Anthropology. \url{https://doi.org/10.5281/zenodo.596403}. \url{http://tsammalex.clld.org}.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Moran, Steven, McCloy, Daniel and Richard Wright (eds). PHOIBLE Online. Leipzig: Max Planck Institute for Evolutionary Anthropology. \url{https://doi.org/10.5281/zenodo.2562767}. \url{http://phoible.org}.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Vaux, Bert, Leemann, Adrian, Wanitsch, Daniel, Moran, Steven, Grimm, Sarah, Robert, Sylvain, Zhakarko, Taras and Scherrer, Yves. US Dialect App. Previously online via Apple App Store. % Online via Apple App Store: \url{http://usdialectapp.com/download}


\vskip 20pt
\begin{flushleft}
{\bf ENCYLOPEDIA ARTICLE (PEER-REVIEWED)}
\end{flushleft}

\hangpara
{\bf 2019}\hspace{1ex}Moran, Steven. Phonological inventories. In \textit{Oxford Research Encyclopedia of Linguistics}. Oxford University Press. \url{http://dx.doi.org/10.1093/acrefore/9780199384655.013.112}.

\clearpage
\vskip 20pt
\begin{flushleft}
{\bf REVIEW ARTICLE}
\end{flushleft}

% Cyberling review of Glottolog

\hangpara
{\bf 2014}\hspace{1ex}Wichmann, S{\o}ren \& Anthony P. Grant (eds). 2012. Quantitative approaches to linguistic diversity: commemorating the centenary of the birth of Morris Swadesh. Amsterdam / Philadelphia: John Benjamins [Benjamins Current Topics 46]. x+182 pp. (ISBN 78 90 272 0265 9) in \textit{Studies in Language} 38(1), 220--233.

\vskip 20pt
\begin{flushleft}
{\bf UNPUBLISHED MANUSCRIPTS, PREPRINTS, AND WORK IN PROGRESS}
\end{flushleft}

\hangpara
van Gijn, Rik, Alena Witzlack-Makarevich and Steven Moran. {\it Typology in Practice}. A course text book for typology using quantitative approaches.

\vskip 6pt
\hangpara
Moran, Steven. \textit{A Grammar of Isaalo (Western Sisaala)}. Unpublished manuscript (work in progress). 117pp. \url{https://github.com/bambooforest/sisaala}.

\vskip 6pt
\hangpara
Moran, Steven. \textit{A Grammatical Sketch of Toro So (Dogon)} (with accompanying French -- English -- Toro So word list). Work in progress which requires additional on-site fieldwork. 

\vskip 6pt
\hangpara
Moran, Steven. \textit{Did speech sounds evolve during human evolution?} Habilitation thesis.

\vskip 6pt
\hangpara
Moran, Steven, Robert Schikowski and Sabine Stoll. ACQDIV Corpus Database User Manual. 92pp. \url{https://github.com/acqdiv/corpus_manual/blob/master/corpus_manual.pdf}

% Unpublished manuscript for ERC project: Acquisition processes in maximally diverse languages: min(d)ing the ambient language. Includes description of the longitudinal corpus data, the extract transform load (ETL) processes for making the data interoperable, and the database design. 


\vskip 20pt
\begin{flushleft}
{\bf INVITED PRESENTATIONS}
\end{flushleft}

\hangpara
{\bf 2021}\hspace{1ex}`Inferring recent evolutionary changes in speech sounds'. \textbf{Keynote} presentation (online) at the 54th Annual Meeting of the Societas Linguistica Europaea. Athens, Greece. With Nicholas A. Lester and Eitan Grossman.

\vskip 6pt
\hangpara
{\bf 2021}\hspace{1ex}`Human speech sounds: three evolutionary timelines'. Paper presented (online) at the Oberseminar in the Seminar für Sprachwissenschaft. July 20, University of Tübingen, Tübingen, Germany.

\vskip 6pt
\hangpara
{\bf 2021}\hspace{1ex}`Investigating the evolution of speech sounds'. Paper presented (online) at the Higher Seminar in Diversity Linguistics. February 4, University of Stockholm, Stockholm, Sweden.

\vskip 6pt
\hangpara
{\bf 2021}\hspace{1ex}`Evolution of speech sounds'. Paper presented (online) at the Workshop on Learnability and Typology
on the Occasion of Klaas Seinhorst’s PhD Defence. February 18. University of Amsterdam, Amsterdam, The Netherlands.

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}`How did speech evolve?'. Paper presented at the Cognitive Science Seminar, University of Neuchâtel. Nov 19, Neuchâtel, Switzerland.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}`ACQDIV project, corpus database, methodological approaches using different types of entropy and statistical regressions'. Paper presented at Emergent constructions -- big data in learner language analyses, University of Basel. May 30, Basel, Switzerland. With Nicholas A. Lester.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}`Building an evolutionary timeline of phonetic features'. Paper presented in the Department of Comparative Cognition in the Institute of Biology, University of Neuchâtel. November 29, Neuchâtel, Switzerland.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}`ACQDIV PHON: Worldwide phoneme frequency predicts age of production'. Paper presented at the ESRC International Centre for Language and Communicative Development (LuCiD) research colloquium. October 3, Manchester, UK. With Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}`Linked Data for Linguistic Research: Phonetics'. Paper presented at the LD4LR workshop for the Dutch CLARIAH project. February 6--7. Utrecht, The Netherlands. \url{https://www.clariah.nl/en/new/blogs/linked-data-for-linguistic-research}

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`The ACQDIV project and database'. Paper presented in the Seminar Series at the Dynamique du Langage lab (DDL) of the Centre national de la recherche scientifique (CNRS). September 21. Lyon, France. With Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`Introduction to ACQDIV corpora'. Workshop: Acquisition processes in maximally diverse languages (ACQDIV). June 10--13. Kappel am Albis, Switzerland.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`Visualizing WALS data'. Workshop: Language Comparison with Linguistic Databases. Organized by the URPP Language and Space at the University of Zurich. April 30. Leipzig, Germany. With Garland McNew.

% https://www.eva.mpg.de/linguistics/conferences/2014-ws-lanclid2/program.html

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`Dogon languages project'. Primera Escuela Latinoamericana de Tipolog{\'i}a y Documentaci{\'o}n Ling{\"u}{\'i}stica. Escuela Nacional de Estudios Superiores, UNAM. March 19--28. Morelia, Mexico.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`Documenting typological diversity for real: the need of language acquisition studies'.  Primera Escuela Latinoamericana de Tipolog{\'i}a y Documentaci{\'o}n Ling{\"u}{\'i}stica. Escuela Nacional de Estudios Superiores, UNAM. March 19--28. Morelia, Mexico. With Dagmar Jung and Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}`Studies in phonological typology with PHOIBLE'. Workshop on Language Comparison with Linguistic Databases: RefLex and Typological Databases. October 7--9. Nijmegen, The Netherlands.
% http://www.mpi.nl/events/language-comparison-with-linguistic-databases-reflex-and-typological-databases/program-abstracts

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}`Linguistic (Linked) Open Data: From collection to application'. \textbf{Keynote} presentation at the workshop on `Collaboration and Computing for Under-resourced Languages in the Linked Open Data Era (CCURL 2014)'. May 26. Reykjavik, Iceland. With Christian Chiarcos.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}`Qualitative analysis and quantitative comparison of Dogon languages'. Paper presented in the Seminar Series at the Dynamique du Langage lab (DDL) of the Centre national de la recherche scientifique (CNRS). January 24. Lyon, France.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Qualitative analysis and quantitative comparison of Dogon languages'. Paper presented in the Seminar Series at the Department of Linguistics, University of Stockholm. December 12. Stockholm, Sweden.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Diversity of Language Sources: Challenges in Digitization, Interoperation and Analysis'. Paper presented at the Language Diversity Congress: Computational Issues in Studying Language Diversity. July 18--20. Groningen, The Netherlands. With Jelena Proki{\'c}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Obstruents and latitude: acoustic adaptation, thermal influence or spurious statistics?'. Poster presented at the Language Diversity Congress: Computational Issues in Studying Language Diversity. July 18--20. Groningen, The Netherlands. With Dami{\'a}n Blasi.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Geolinguistic Diffusion of Language Change'. Paper presented at the Simulation of Diachrony workshop. November 5--6. Zurich, Switzerland. With Jelena Proki{\'c}.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Research Unit: Quantitative Language Comparison'. Paper presented at the RefLex meeting (CNRS). June 5--7. Lyon, France. 

\vskip 6pt
\hangpara
{\bf 2011}\hspace{1ex}`Technological infrastructure for comparative linguistics and linguistic fieldwork: some case studies'. Paper presented at the Max Planck Institute for Evolutionary Anthropology. January 27, Leipzig, Germany. 

\vskip 6pt
\hangpara
{\bf 2008}\hspace{1ex}`The e-Linguistics Toolkit'. Paper presented at the Institute for Language Information and Technology (The Linguist List). December 18, Ypsilanti, Michigan. With Scott Farrar.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}`From Documentation to Computation'. Paper presented at the Max Planck Institute for Evolutionary Anthropology. September 13, Leipzig, Germany.


\vskip 20pt
\begin{flushleft}
{\bf REFEREED PRESENTATIONS}
\end{flushleft}

\hangpara
{\bf 2021}\hspace{1ex}`Temporal bias: a new kind of bias for typologists to worry about'. Paper presented at the 5th Usage-Based Linguistic Conference (UBL 5). July 5--7, (online) Tel Aviv, Israel. With Eitan Grossman.

\hangpara
\vskip 6pt
{\bf 2021}\hspace{1ex}`Defining and operationalizing	 `borrowability' in phonology'. Paper presented at the 5th Usage-Based Linguistic Conference (UBL 5). July 5--7, (online) Tel Aviv, Israel. With Elad Eisen, Eitan Grossman, and Dmitry Nikolaev.

\hangpara
\vskip 6pt
{\bf 2021}\hspace{1ex}`Defining and operationalizing	 `borrowability' in phonology'. Paper presented at the 28th Manchester Phonology Meeting. May 26--28, (online) Manchester, UK. With Elad Eisen, Dmitry Nikolaev and Eitan Grossman.

\hangpara
\vskip 6pt
{\bf 2019}\hspace{1ex}`The typology of phonological segment borrowing'. Paper presented at the 
13th Conference of the Association for Linguistic Typology. September 4--6, Pavia, Italy. With Eitan Grossman, Dmitry Nikolaev, Elad Eisen, Ronén Júda, Schwartz Layla and Yoav Yosef.

\hangpara
\vskip 6pt
{\bf 2019}\hspace{1ex}`How different were phonological distributions?
The typology of phonological segment borrowing and the Uniformitarian
Assumption'. Paper presented at the 52nd Annual Meeting of the Societas Linguistica Europaea. August 21--24, Leipzig, Germany. With Eitan Grossman and Dmitry Nikolaev.

\hangpara
\vskip 6pt
{\bf 2019}\hspace{1ex}`What contact typologists want from grammatical descriptions'. Paper presented at Descriptive grammars and typology: The challenges of writing grammars of underdescribed and endangered languages. March 27--29, Helsinki, Finland. With Eitan Grossman.

\hangpara
\vskip 6pt
{\bf 2018}\hspace{1ex}`Variation sets in maximally diverse languages'. Poster presented at the 43rd Boston University Conference on Language Development (BUCLD). November 2--4, Boston, USA. With Sabine Stoll.

\hangpara
\vskip 6pt
{\bf 2018}\hspace{1ex}`Acquisition processes in maximally diverse languages: min(d)ing the ambient language'. Paper presented at the Days of Swiss Linguistics. October 12, Bern, Switzerland. With Sabine Stoll, Damian Blasi, Dagmar Jung and Jekaterina Mazara.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}`Worldwide frequency distribution of phoneme types predicts their order of acquisition'. Paper presented at the 51st Annual Meeting of the Societas Linguistica Europaea (SLE). August 29--September 1, Tallinn, Estonia. With Sebastian Sauppe, Nicholas A. Lester and Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}`Comparative corpus linguistics: New perspectives and applications'. Paper presented at the 51st Annual Meeting of the Societas Linguistica Europaea (SLE). August 29--September 1, Tallinn, Estonia. With Natalia Levshina and Annemarie Verkerk.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}`Cross-linguistically Small World Networks are Ubiquitous in Child-directed Speech'. Paper presented at the Eleventh International Conference on Language Resources and Evaluation (LREC 2018). May 7--12, Miyazaki, Japan. With Danica Pajovi{\'c} and Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}`BDPROTO: A Database of Phonological Inventories from Ancient and Reconstructed Languages'. Paper presented at the Eleventh International Conference on Language Resources and Evaluation (LREC 2018). May 7--12, Miyazaki, Japan. With Egidio Marsico, Sebastien Flavier and Annemarie Verkerk.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}`Towards faithfully visualizing global linguistic diversity'. Paper presented at the Eleventh International Conference on Language Resources and Evaluation (LREC 2018). May 7--12, Miyazaki, Japan. With Garland McNew and Curdin Derungs.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}`Differential rates of change in consonant and vowel systems'. Paper presented at the 12th International Conference on the Evolution of Language (EVOLANGXII). April 16--19, Toru{\'n}, Poland. With Annemarie Verkerk. % doi:10.12775/3991-1.077

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}`Probing the biological conditions for modern phonologies: The late emergence of labiodentals'. Paper presented at the 12th International Conference on the Evolution of Language (EVOLANGXII). April 16--19, Toru{\'n}, Poland. With Dami{\'a}n Blasi, Scott Moisik, Ani Margvelashvili, Paul Widmer, Dan Dediu and Balthasar Bickel.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}`Phylogenesis of phonetic features'. Paper presented at the 12th Conference of the Association for Linguistic Typology (ALT). December 11--15, Canberra, Australia.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}`Probing the biological conditions for modern phonologies: the late emergence of labiodentals'. Paper presented at the 48th annual meeting of the Australian Linguistics Society (ALS). December 4--7, Sydney, Australia. With Dami{\'a}n Blasi, Scott Moisik, Ani Margvelashvili, Paul Widmer, Dan Dediu and Balthasar Bickel.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}`Worldwide frequency of phonemes predicts their age of acquisition'. Poster presented at the 42nd Boston University Conference on Language Development (BUCLD). November 3--5, Boston, USA. With Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}`The Unicode Cookbook for Linguists'. Paper presented at the 47th Pozna{\'n} Linguistic Meeting. September 18--20, Pozna{\'n}, Poland. With Michael Cysouw. 
% http://wa.amu.edu.pl/plm/2017/files/abstracts/PLM2017_Abstract_Moran.pdf

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex} `Molecular Anthropology as a window on language contact: diffusion probabilities in phonology and grammar'. Paper presented at the 50th Annual Meeting of the Societas Linguistica Europaea (SLE). September 10--13, Zurich, Switzerland. With Balthasar Bickel, Dami{\'a}n Blasi and Brigitte Pakendorf.
 
\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}`Probing the biological conditions for modern phonologies: the late emergence of labiodentals'. Paper presented at the 50th Annual Meeting of the Societas Linguistica Europaea (SLE). September 10--13, Zurich, Switzerland. With Dami{\'a}n Blasi, Scott Moisik, Ani Margvelashvili, Paul Widmer, Dan Dediu and Balthasar Bickel.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}`Introduction to the SLE workshop: Non-linguistic causes of linguistic diversity'. Paper presented at the 50th Annual Meeting of the Societas Linguistica Europaea (SLE). September 10--13, Zurich, Switzerland. With Antonio Benítez-Burraco and Dan Dediu.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}`Investigating the phylogenesis of phonetic features'. Poster presented at the 25th Manchester Phonology Meeting. May 25--27, Manchester, UK.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}`Evaluating information loss from phonological dimensionality reduction'. Paper presented at The Role of Predictability in Shaping Human Language Sound Patterns (satellite event at the 16th Speech Science and Technology Conference). December 10--11, Sydney, Australia. With Jayden Macklin-Cordes and Erich Round.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}`Frequent frames in maximally diverse languages'. Paper presented at the Boston University Conference on Language Development (BUCLD). November 4--6, Boston, USA. With Dami{\'a}n Blasi and Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}`How to study variation in language acquisition: a new cross-linguistic corpus approach'. Paper presented at the 9th Days of Swiss Linguistics. June 29--July 1, Geneva, Switzerland.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}`Visualizing development in longitudinal language acquisition data'. Poster presented at the 9th Days of Swiss Linguistics. June 29--July 1, Geneva, Switzerland. With Danica Pajovi{\'c}, Jekaterina Mazara and Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}`The ACQDIV Database: Min(d)ing the Ambient Language'. Paper presented at the Tenth International Conference on Language Resources and Evaluation (LREC 2016). May 23--28, Portoro{\v z}, Slovenia. With Robert Schikowski, Danica Pajovi{\'c}, Cazim Hysi and Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`Syntactic mixing across generations in an environment of community-wide bilingualism'. Paper Presented at 48th Annual Meeting of the Societas Linguistica Europaea (SLE). September 2--5. Leiden, The Netherlands. With Balthasar Bickel, Taras Zakharko, Robert Schikowski and Sabine Stoll.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`Phonological features from a quantitative typological perspective'. Paper Presented at the Conference: Diversity Linguistics: Retrospect and Prospect. May 1--3. Leipzig, Germany. With Balthasar Bickel and Taras Zakharko.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`Tsammalex'. Paper Presented at the Conference: Diversity Linguistics: Retrospect and Prospect. May 1--3. Leipzig, Germany. With Christfried Naumann, Robert Forkel and Lena Sell.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`Syntactic mixing across generations in a Chintang/Nepali bilingual environment'. Paper Presented at the Conference: Diversity Linguistics: Retrospect and Prospect. May 1--3. Leipzig, Germany. With Sabine Stoll, Taras Zakharko, Robert Schikowski and Balthasar Bickel.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}`Subject agreement suspension and information structure: a view from Dogon languages'. Paper Presented at 8th Days of Swiss Linguistics. June 19--21. Zurich, Switzerland. With Giorgio Iemmolo.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}`Average in phonological typology: phoneme inventories'. Paper Presented at 8th Days of Swiss Linguistics. June 19--21. Zurich, Switzerland. With Taras Zakharko.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}`Structural diversity in phonological systems'. Paper Presented at 8th Days of Swiss Linguistics. June 19--21. Zurich, Switzerland. With Balthasar Bickel and Taras Zakharko.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}`A Crowdsourcing Smartphone Application for Swiss German: Putting Language Documentation in the Hands of the Users'. Poster presented at LREC 2014. May 26--31. Reykjavik, Iceland. With Jean-Philippe Goldman, Adrian Leemann, Marie-Jos{\'e} Kolly, Ingrid Hove, Ibrahim Almajai and Volker Dellwo.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Lemon-aid: using Lemon to aid quantitative historical linguistic analysis'. Paper presented at the 2nd Workshop on Linked Data in Linguistics: Representing and linking lexicons, terminologies and other language data. September 23. Pisa, Italy. With Martin Brümmer. 

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Linguistic Resources Enhanced with Geospatial Information'. Paper presented at the 2nd Workshop on Linked Data in Linguistics: Representing and linking lexicons, terminologies and other language data. September 23. Pisa, Italy. With Richard Littauer and Boris Villazon-Terrazas.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Cross-linguistic Comparison of Complexity Measures in Phonological Systems'. Paper Presented at the 44th Pozna{\'n} Linguistic Meeting (PLM 2013). August 29--September 1. Pozna{\'n}, Poland. With Dami{\'a}n Blasi.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Application and Evaluation of Quantitative Comparative Methods on Dogon'. Paper presented at the Colloquium on African Languages and Linguistics (CALL). August 26--28. Leiden, The Netherlands. With Jelena Proki{\'c}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Estimating Diachronic Preferences of Phonological Features Cross-linguistically'. Paper Presented at the Association for Linguistic Typology. August 15--18. Leipzig, Germany. With Taras Zakharko and Balthasar Bickel.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`￼Typology with Graphs and Matrices'. Paper Presented at the Association for Linguistic Typology. August 15--18. Leipzig, Germany. With Michael Cysouw.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`￼An Open Source Toolkit for Quantitative Historical Linguistics'. Paper Presented at the Association for Computational Linguistics. August 4--9. Sofia, Bulgaria. With Johann-Mattis List.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Digital technology and endangered Dogon languages'. Paper Presented at 19th LIPP-Symposium: Gef{\"a}hrdete Sprachen. July 10--12. Munich, Germany. With Jelena Proki{\'c}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Revisiting ``The role of features in phonological inventories'''. Paper presented at the CUNY Conference on the Feature in Phonology and Phonetics. January 16--18. New York, NY. With Daniel McCloy and Richard Wright. \url{http://dan.mccloy.info/pubs/McCloyEtAl2013_cunyFeatureConf.pdf}.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Automatic Detection of Borrowings in Lexicostatistic Datasets: A Workflow for Automatic Linguistic Reconstruction'. Paper Presented at the Workshop on Quantitative Approaches to Areal Typology. December 13--14. Amsterdam, Netherlands. With Johann-Mattis List and Jelena Proki{\'c}.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`A Python Toolkit for Quantitative Tasks in Historical-Comparative Linguistics'. Paper Presented at the Phylometric and Phylogenetic Approaches in the Humanities Workshop. November 24. Bern, Switzerland. With Johann-Mattis List.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Investigating the Genealogical Relatedness of the Dogon Languages'. Paper Presented at the Biological Evolution and Diversification of Languages Workshop [BEDLAN]. September 19--21. University of Turku, Finland. With Jelena Proki{\'c}.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Dogon classification'. Paper presented at Proto-Niger-Congo: Comparison and Reconstruction International Congress. September 18--21. Paris, France. With Kirill Prokhorov and Jeffrey Heath.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`A Python Library for Historical Comparative Linguistics'. Paper presented at EuroSciPy 2012. August 23--27. Brussels, Belgium. With Johann-Mattis List. \textbf{Awarded best paper.}

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Investigating the Genealogical Relatedness of the Endangered Dogon Languages'. Paper presented at Digital Humanities 2012. July 16--22. Hamburg, Germany. With Jelena Proki{\'c}.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Using Linked Data to create a typological knowledge base'. Paper presented at Linked Data in Linguistics (DGfS 2012). March 6--9. Frankfurt, Germany.

\vskip 6pt
\hangpara
{\bf 2011}\hspace{1ex}`Black box statistical approaches'. Paper presented at the Workshop on Comparing Approaches to Measuring Linguistic Differences. October 24--25. Gothenburg, Sweden. With Jelena Proki{\'c}.

\vskip 6pt
\hangpara
{\bf 2011}\hspace{1ex}`Phonemic Inventories as a Phylogenetic Characteristic'. Paper presented at the 20th International Conference on Historical Linguistics (ICHLXX). July 25--30, Osaka, Japan. With Michael Cysouw.

\vskip 6pt
\hangpara
{\bf 2011}\hspace{1ex}`Oblique Cases and Semantic Roles'. Paper presented at the Workshop on Semantic Role Complexes: (New) Approaches to Defining Semantic Roles. April 4--5, Zurich, Switzerland. With Jeffrey Heath.

\vskip 6pt
\hangpara
{\bf 2009}\hspace{1ex}`Dogon Linguistics and Typology on the Web'. Poster presented at the Association for Linguistic Typology (ALT08). July 24--25, Berkeley, California. With Laura McPherson.

\vskip 6pt
\hangpara
{\bf 2009}\hspace{1ex}`The Dogon Languages of Mali'. Paper presented at the Annual Conference on African Linguistics (ACAL). April 9--12, Indiana University, Bloomington, Indiana. With Jeffrey Heath and Abbie Hantgan.

\vskip 6pt
\hangpara
{\bf 2008}\hspace{1ex}`The e-Linguistics Toolkit'. Paper presented at e-Humanities --- an emerging discipline: Workshop in the 4th IEEE International Conference on e-Science. December 10, Indianapolis, Indiana. With Scott Farrar.

\vskip 6pt
\hangpara
{\bf 2008}\hspace{1ex}`From the Field to the World'. Paper presented at the 20th Northwest Linguistics Conference (NWLC). May 3--4, Seattle, Washington. With Naomi Fox.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}`Moodle: A CALL Environment for Language Documentation and Revitalization'. Poster presented at the 2nd annual Conference on Endangered Languages and Cultures of Native America (CELCNA). March 31--April 2, Salt Lake City, Utah.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}`Best Practices in Practice: Documentation of Western Sisaala'. Poster presented at the annual meeting of the Linguistic Society of America, January 5--8, Albuquerque, New Mexico.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}`APEC: A tool for automatic phonological analysis of field data'. Software demonstration at the E-MELD Workshop on Digital Language Documentation, Tools and Standards: the state of the art. June 20--22, Lansing, Michigan. With Shauna Eggers.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}`Creating a Video Clip Resource to Enhance Linguistics Courses'. Poster presented at the University of Washington Teaching and Learning Symposium. April 25, Seattle, Washington. With Sharon Hargus.

\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}`Creating Language Resources that Last: The E-MELD School of Best Practices in Digital Language Documentation'. Poster presented at the 2005 LSA Summer Institute event: Language Documentation: Theory, Practice, and Values. July 9--11. Harvard University, Cambridge, Massachusetts. With Helen Aristar-Dry, Antony Aristar, Naomi Fox, Susan Hooyenga and Megan Zdrojkowski.

\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}`Ensuring that Digital Data Last: Archiving and Linguistic Resources'. Paper presented at the 34th annual meeting of the Linguistic Association of the Southwest. October 7--9, Lubbock, Texas. 
 
\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}`Creating Language Resources that Last: The E-MELD Project and Best Practices in Digital Language Documentation'. Poster presented at the E-MELD Workshop 2005: Linguistic Ontologies and Data Categories for Linguistic Resources, July 1--3, Cambridge, Massachusetts. With Susan Hooyenga and Megan Zdrojkowski.

\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}`The E-MELD School of Best Practices in Digital Language Documentation'. Paper presented at the 41st annual meeting of the Chicago Linguistics Society 41. April 7--9, Chicago, Illinois.

\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}`Endo and Exocentric Compounding in Western Sisaala'. Paper presented at the 31st annual meeting of the Berkeley Linguistics Society. February 18--20, Berkeley, California.

\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}`Challenges in Fieldwork: Review of Databases for Linguistic Purposes'. Poster presented at the annual meeting of the Linguistic Society of America. January 6--9, Oakland, California.
% Committee on Endangered Languages and their Preservation. 

\vskip 6pt
\hangpara
{\bf 2004}\hspace{1ex}`Review of DBMS for Linguistic Purposes'. Paper presented at the E-MELD Conference 2004: Linguistic Databases and Best Practice. July 15--18, Detroit, Michigan. With Marisa Ferrara.

\vskip 6pt
\hangpara
{\bf 2002}\hspace{1ex}`English Loanwords in Maori'. Paper presented at the Eastern Michigan University Undergraduate Symposium. March 22, Ypsilanti, Michigan.


\vskip 20pt
\begin{flushleft}
{\bf NON-REFEREED PRESENTATIONS}
\end{flushleft}

\hangpara
{\bf 2019}\hspace{1ex}`Current research in phonological typology: Introduction'. Paper presented at the 13th Conference of the Association for Linguistic Typology. September 4--6, Pavia, Italy. With Eitan Grossman.

\hangpara
\vskip 6pt
{\bf 2016}\hspace{1ex}`Tracing the origin of human speech sounds: evolutionary and historical perspectives'. Paper presented at the Genetics and Animal Communication Workshop hosted by the University Research Priority Program: Evolution in Action. November 21--22, Zurich, Switzerland. With Balthasar Bickel, Dami{\'a}n Blasi and Paul Widmer.

\hangpara
\vskip 6pt
{\bf 2016}\hspace{1ex}`Statistical Signals of the Trans-Pacific Migrations in Language'. Paper presented at the Linguistics and Genetics Workshop in Zurich 2016. University of Zurich. March 13. Authors: Balthasar Bickel, Curdin Derungs, Steven Moran, Sean Roberts and Dan Dediu.

\hangpara
\vskip 6pt
{\bf 2015}\hspace{1ex}`Making the data usable: issues in unifying language acquisition corpora'. Paper presented at the Inter-Lab Workshop on Data and Standards: How to make data reusable? University of Zurich. May 29. With Robert Schikowski.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}`ACQDIV: data, infrastructure, future'. Paper Presented at the Research Colloquium of the Department of Comparative Linguistics at the University of Zurich. May 22.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}`Language Geography and Dogon'. Paper Presented at the Maps and Grammar Workshop at the University of Zurich. March 21. With Curdin Derungs and Simon Etter.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Estimating Diachronic Preferences of Phonological Features Cross-linguistically'. Paper Presented at the Research Colloquium of the General Department of Linguistics at the University of Zurich. October 25. With Taras Zakharko and Balthasar Bickel.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Research Unit: Quantitative Language Comparison'. Paper presented at the Institute for Language Information and Technology (The Linguist List). September 12, Ypsilanti, Michigan.

\vskip 6pt
\hangpara
{\bf 2011}\hspace{1ex}`Orthography Profiles'. Paper presented at the Phonetics Lab Meeting, LMU, M{\"u}nchen. May 18, Munich, Germany. With Jelena Proki{\'c}.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}`Benefits for Using the LKB and Grammar Engineering for Field Linguists'. Paper presented at the 2nd annual Deep Linguistic Processing with HPSG (DELPH-IN) meeting. June 12--17, Fefor, Norway.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}`The E-MELD Project and Tools for Field Linguists'. Demo presented at the Microsoft / UW Symposium in Computational Linguistics. February 3, Redmond, Washington.


\vskip 20pt
\begin{flushleft}
{\bf TEACHING EXPERIENCE}
\end{flushleft}

\begin{flushleft}
{\bf University courses (instructor)}
\end{flushleft}

% Co-lecturer in Integrative Models, Cognitive Science Masters Program, University of Neuchâtel, 2020
% Guest lecturer in Human Evolution Seminar, University of Neuchâtel, 2020
% Quantitative Methods and Applications in Linguistics

\hangpara Introduction to First Language Acquisition from a Cross-linguistic Perspective (301: Einf{\"u}hrung in die Spracherwerbsforschung). University of Zurich, Spring 2019 \& Spring 2016.

\vskip 6pt
\hangpara The Nature and Evolution of Phonology (605: Sprachvergleich). University of Zurich, Fall 2018.

\vskip 6pt
\hangpara Linguistic Field Methods (501: Feldforschungsmethoden). University of Zurich, Fall 2017 (Ga language) \& Fall 2016 (Akan language).

\vskip 6pt
\hangpara Anthropological Linguistics: Social and Cultural Perspectives (302a: Ethnolinguistik). University of Zurich, Fall 2015.

\vskip 6pt
\hangpara Qualitative and Quantitative Analysis (102: Methoden und Anwendungen). University of Zurich, Spring 2015 \& Fall 2013.

\vskip 6pt
\hangpara Introduction to Anthropological Linguistics (302: Ethnolinguistik). University of Zurich, Fall 2014. Taught with Balthasar Bickel.

% seminar Text manipulation (LING 481)
% \hangpara
\vskip 6pt
\hangpara Introduction to Morphology (LING 481). University of Washington, annually 2007--2010.

\begin{flushleft}
{\bf University courses (teaching assistant)}
\end{flushleft}
% {\bf 2010 Teaching Assistant:}\hspace{1ex} (LING 571)
\hangpara Deep Processing Techniques for Natural Language Processing (LING 571). University of Washington. Winter 2010 \& 2009.

\vskip 6pt
\hangpara % {\bf 2010 Teaching Assistant:}\hspace{1ex}  (CSE/LING 472)
Introduction to Computational Linguistics (CSE/LING 472). University of Washington. Spring 2010.

\begin{flushleft}
{\bf Summer schools (instructor)}
\end{flushleft}
\hangpara Methods and practical applications for language documentation (M{\'e}tods e instruments pr{\'a}cticos para la documentaci{\'o}n ling{\"u}{\'i}stica, with Heriberto Avelino). Primera Escuela Latinoamericana de Tipolog{\'i}a y Documentaci{\'o}n Ling{\"u}{\'i}stica Alemania-M{\'e}xico. Nacional de Estudios Superiores, UNAM. Morelia, Mexico. March 23--28, 2015.

\vskip 6pt
\hangpara Database Design for Linguists. Quantitative Analysis of Linguistic Data (QUALD) doctoral seminar, University of Zurich, Summer 2014.

\clearpage

\vskip 20pt
\begin{flushleft}
{\bf ADVISING}
\end{flushleft}

\hangpara
{\bf 2021}\hspace{1ex}Klaas Seinhorst, PhD. \href{https://www.fon.hum.uva.nl/klaas/KlaasSeinhorstDissertation.pdf}{The complexity and learnability of phonological patterns: simulations, experiments, typology}. PhD thesis committee. University of Amsterdam.

\hangpara
\vskip 6pt
{\bf 2020}\hspace{1ex}Elad Eisan. \href{https://www.researchgate.net/publication/341734023_The_Typology_of_Phonological_Segment_Borrowing}{
The Typology of Phonological Segment Borrowing}. M.A.\ thesis committee. Department of Linguistics, The Hebrew University of Jerusalem.

\hangpara
\vskip 6pt
{\bf 2019}\hspace{1ex}Cazim Hysi. Implementing Diachronic Language Simulation in Python. B.A.\ thesis committee. Department of Computational Linguistics, University of Zurich.

\hangpara
\vskip 6pt
{\bf 2016}\hspace{1ex}Danica Pajovi{\v c}. ACQDIVIZ: Visualising Development in Longitudinal First Language Acquisition Data. M.A.\ thesis committee. Department of Computational Linguistics, University of Zurich.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}Melanie Widmer. Die Rolle distributioneller Information im Spracherwerb: Kategorisierung mit Hilfe von h{\"a}ufigen Frames. B.A.\ thesis committee. Department of Comparative Linguistics, University of Zurich.


\vskip 20pt
\begin{flushleft}
{\bf RESEARCH PROJECT TEAM MEMBER}
\end{flushleft}

% BCS-0537435 (2006-09), BCS-0853364 (2009-13), and BCS-1263150 (2013-16), PI Jeffrey Heath. 
\hangpara
{\bf 2020}\hspace{1ex}Non-randomness in Morphological Diversity: A Computational Approach Based on Multilingual Corpora. Swiss National Science Foundation. Primary Investigator (PI) Tanja Samardzic (U. Zurich). Positions: postdoctoral researcher and technical project manager. \url{http://p3.snf.ch/project-176305}. Project homepage: \url{https://www.spur.uzh.ch/en/departments/research/textgroup/MorphDiv.html}.

\vskip 6pt
\hangpara
{\bf 2014--2019}\hspace{1ex}ACQDIV: Acquisition processes in maximally diverse languages: Min(d)ing the ambient language. European Research Council Consolidator Grant ERC-2013-CoG, SH4, RCN: 615988. PI Sabine Stoll (U. Zurich). Positions: postdoctoral researcher and technical project manager. \url{https://cordis.europa.eu/project/rcn/191230/}. Project homepage: \url{http://www.acqdiv.uzh.ch}. % 1,998,438 EUR

\vskip 6pt
\hangpara
{\bf 2013--2016}\hspace{1ex}Investigating the interaction of tone and syntax in the Bagime and the Dogon languages of Mali and Burkina Faso (NSF) award no.\ BCS-1263150. PI Jeffrey Heath (U. Michigan). Positions: field researcher and technical lead. \url{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1263150}. Project webpages: \url{http://dogonlanguages.org} \& \url{http://tsammalex.clld.org/}.
% $344,349.00

\vskip 6pt
\hangpara
{\bf 2010--2014}\hspace{1ex}Quantitative modeling of historical-comparative linguistics: Unraveling the phylogeny of native South American languages (QuantHistLing). European Research Council Starting Grant ERC-2009-StG, SH4, RCN: 191230. PI Michael Cysouw (U. Marburg). Position: postdoctoral researcher. \url{https://cordis.europa.eu/project/rcn/93461/}.
% 1,938,000 EUR

\vskip 6pt
\hangpara
{\bf 2009--2013}\hspace{1ex}Dogon Languages of Mali. National Science Foundation (NSF) award no.\ BCS-0853364. PI Jeffrey Heath. Positions: field researcher and technical lead. \url{https://www.nsf.gov/awardsearch/showAward?AWD_ID=0853364}.
% $317,421.00

\vskip 6pt
\hangpara
{\bf 2009--2010}\hspace{1ex}Phonetics Information Base and Lexicon (PHOIBLE). UW Royalty Research Fund Grant. PI Richard Wright (U. Washington). Positions: lead developer and project manager. \url{http://phoible.org/}
% $30,000

\vskip 6pt
\hangpara
{\bf 2008--2010}\hspace{1ex}Lexicon Integration with the Gold Ontology (LEGO). National Science Foundation (NSF) award no.\ BCS-0753321. PIs Helen Aristar-Dry (EMU) and Jeff Good (U. Buffalo). Positions: programmer and data provider. \url{https://www.nsf.gov/awardsearch/showAward?AWD_ID=0753321}. Project homepage: \url{http://lego.linguistlist.org/}.
% $636,443

\vskip 6pt
\hangpara
{\bf 2008--2009}\hspace{1ex}GOLD Community of Practice: Laying the Foundations for a Linguistics Cyberinfrastructure. National Science Foundation (NSF) award no.\ BCS--0720670. PI Scott Farrar. Positions: programmer and researcher. \url{https://www.nsf.gov/awardsearch/showAward?AWD_ID=0720670}. % $147,457.00

\vskip 6pt
\hangpara
{\bf 2006--2009}\hspace{1ex}Languages of the Dogon. National Science Foundation (NSF) award No.\ BCS-0537435. PI Jeffrey Heath. Position: field researcher and technical lead. \url{https://www.nsf.gov/awardsearch/showAward?AWD_ID=0537435}.
% $209,961

\vskip 6pt
\hangpara
{\bf 2004--2005}\hspace{1ex}Creating a Grammar, Dictionary, and Texts of the Dogon Languages of Mali, West Africa. National Endowment for the Humanities (NEH) award no.\ PA-50643. PI Jeffrey Heath. Position: programmer.

\vskip 6pt
\hangpara
{\bf 2003--2005}\hspace{1ex}Description of Chorote, Nivacl{\'e} and Kadiw{\'e}u: three of least known and most endangered languages of the Chaco. Endangered Languages Documentation Programme (Rausing Charitable Fund), SOAS, University of London. PIs Lyle Campbell (U. Utah), Ver{\'o}nica Grondona (EMU) and Filomena Sandalo (IEL-Unicamp). Position: programmer.

\vskip 6pt
\hangpara
{\bf 2001--2005}\hspace{1ex}Electronic Metastructure for Endangered Languages Data (E-MELD). National Science Foundation (NSF) award No.\ BCS-0094934. PIs Helen Aristar-Dry and Anthony Aristar (WSU). Positions: project manager and lead web developer. \url{https://www.nsf.gov/awardsearch/showAward?AWD_ID=0094934}. Project homepage: \url{http://emeld.org/}
% $2,142,913.00


\vskip 20pt
\begin{flushleft}
{\bf GUEST RESEARCHER}
% VISITING SCIENTIST
\end{flushleft}
\begin{tabular}{lp{5.5in}}
\bf 2020--2021	& {\bf Department of Anthropology} \\
& University of Zurich, Zurich, Switzerland. \\
\bf 2020--2021	& {\bf Department of Comparative Language Science} \\
& University of Zurich, Zurich, Switzerland. \\
\bf 2010	& {\bf Department of Linguistics}\\
& Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany (January).  \\
\bf 2006	& {\bf Department of Linguistics}\\
& Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany (August--September).  \\
\end{tabular}

\vskip 24pt
\begin{flushleft}
{\bf TECHNICAL SKILLS (PAST \& PRESENT)}
\end{flushleft}
\begin{itemize}
\item Basic statistics, Command line, Coldfusion, CSS, Git, HTML, Javascript, Jupyter, \LaTeX, Linked Data, Linux, Markdown, MySQL, OS X, OWL, Photoshop, PHP, Python, R, RDF, SPARQL, SQL, Unix, XML
\item Extensive experience in: the Unicode Standard and multilingual character encodings, text processing and data mining, orthographic segmentation, syntactic \& semantic data interoperation, database design and implementation, web applications development, digital archiving \& digitizing language documentation and multimedia, qualitative and quantitative analysis
\item For various coding projects, see: \url{https://github.com/bambooforest/}
\item Data creator and curator of PHOIBLE Online (\url{http://phoible.org/}), a broad coverage cross-linguistic database of phonological inventory data on sounds of the world's languages
\item Data contributor and curator the Dogon and Bangime Linguistics project website (\url{http://dogonlanguages.org/}), a comprehensive multilingual and multimedia resource on the Dogon language family in Mali
\end{itemize}

\vskip 10pt
\begin{flushleft}
{\bf FIELDWORK}
\end{flushleft}
\begin{itemize}
\item {\bf Toro So} (Dogon; ISO 639-3: dts) in Bobo-Dioulasso, Burkina Faso (Mali unsafe during this period, 2013); continuation of grammar and dictionary development
\item {\bf Toro So} in Douentza and Sangha, Mali (2009); initial English--French--Toro So dictionary and grammar development
\item {\bf Western Sisaala} (Niger-Congo; Gur; ISO 639-3: ssl) in Lambussie, UWR, Ghana (2003); orthography, dictionary and grammar development; extensive grammatical knowledge
\end{itemize}

\vskip 10pt
\begin{flushleft}
{\bf LANGUAGES}
\end{flushleft}
\begin{itemize}
\item {\bf English} native
\item {\bf German} proficient
\item {\bf French} basic
\item {\bf Toro So} extensive grammatical knowledge through on-site fieldwork
\item {\bf Sisaala} extensive grammatical knowledge through on-site fieldwork
\item {\bf Akan} taught field methods course
\item {\bf Ga} taught field methods course
\item {\bf Tigrinya} field methods course participant
\item {\bf Sisaala} field methods course participant
\end{itemize}

% PRESENTATIONS
% Linguistic Resources enhanced with geospatial Information
% Steven Moran, Richard Littauer, and Didier Cherex and Boris Villazón-Terrazas
% http://www.slideshare.net/boricles@boricles

\vskip 10pt
\begin{flushleft}
{\bf INVITED PARTICIPANT}
\end{flushleft}

\hangpara
{\bf 2017}\hspace{1ex}`Quantitative Methods - Spring School 2017', sponsored by the Max Planck Institute for the Science of Human History (MPI SSH). May 8--14. Jena, Germany.

\hangpara
\vskip 6pt
{\bf 2017}\hspace{1ex}`LD4LR: Linked Data for Linguistic Research', sponsored by the Common Lab Research Infrastructure for the Arts and Humanities (CLARIAH) initiative. February 6--7. Utrecht, The Netherlands. \url{https://www.clariah.nl/en/new/blogs/linked-data-for-linguistic-research}.

\hangpara
\vskip 6pt
{\bf 2015}\hspace{1ex}`Workshop on Language Comparison with Linguistic Databases', sponsored by the Max Planck Institute for Evolutionary Anthropology. April 30. Leipzig, Germany. \url{https://www.eva.mpg.de/linguistics/conferences/2014-ws-lanclid2/index.html}.

\hangpara
\vskip 6pt
{\bf 2014}\hspace{1ex}`Workshop on Language Comparison with Linguistic Databases: RefLex and Typological Databases', sponsored by the Max Planck Institute for Psycholinguistics. October 7--9. Nijmegen, The Netherlands. \url{http://www.mpi.nl/events/language-comparison-with-linguistic-databases-reflex-and-typological-databases}.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Simulation of Diachrony', sponsored by the Department of General Linguistics, University of Zurich. November 5--6. Zurich, Switzerland.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Multilingual Web Workshop: Linked Open Data and Multilingual Web-LT Requirements', sponsored by the World Wide Web Consortium (W3C), Trinity College Dublin, and the European Commission. June 11--13. Dublin, Ireland. \url{https://www.multilingualweb.eu/documents/dublin-workshop/dublin-cfp}.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Typological databases in RDF', sponsored by the Max Planck Institute for Evolutionary Anthropology. March 14--15, Leipzig, Germany. 

\vskip 6pt
\hangpara
{\bf 2009}\hspace{1ex}`Cyberling 2009', sponsored by the Linguistic Society of America, the US National Science Foundation, and the University of California, Berkeley. July 17--19. Berkeley, California. \small\url{https://www.linguisticsociety.org/sites/default/files/Cyberling2009Workshop_FinalReport.pdf}.

\vskip 6pt
\hangpara
{\bf 2009}\hspace{1ex}`Dogon Dictionary Development', sponsored by the Centre National de la Recherche Scientifique et Technologique (CNRST), Mali. June 8--10, Bamako, Mali, West Africa. Workshop coordinator with Jeffrey Heath.

\vskip 6pt
\hangpara
{\bf 2009}\hspace{1ex}`Lexicon Integration with the Gold Ontology (LEGO)', sponsored by the Institute for Language Information and Technology and Eastern Michigan University. March 6--8, Ypsilanti, Michigan.

\vskip 6pt
\hangpara
{\bf 2007}\hspace{1ex}`Toward the Interoperability of Language Resources -- Working group on Lexicon Schemas and Related Data Models', sponsored by the US National Science Foundation, Stanford University, the University of Kansas, Eastern Michigan University, and The Linguist List. July 13--15, Stanford University, Palo Alto, California.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}`Digital Tools Summit in Linguistics (DTSL)', sponsored by the US National Science Foundation. Working group on Fieldwork and Archiving. June 22--23, Lansing, Michigan.


\vskip 20pt
\begin{flushleft}
{\bf AWARDS}
\end{flushleft}

\hangpara
{\bf 2013}\hspace{1ex}Nominated for the E.W. Beth Dissertation Prize for outstanding dissertations in the fields of Logic, Language, and Information (FoLLI---the Association for Logic, Language, and Information) by Professors Emily Bender and Richard Wright (UW).

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Nominated for the University of Washington's Graduate School Distinguished Dissertation Award 2013 by the UW Linguistics Department (one nomination annually per department).

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}Awarded best paper for `A Python Library for Historical Comparative Linguistics' (with Johann-Mattis List), presented at EuroSciPy 2012. August 23--27. Brussels, Belgium.

\vskip 6pt
\hangpara
{\bf 2010}\hspace{1ex}Excellence in Linguistic Research Graduate Award, Linguistics Department, University of Washington. \textbf{One award annually}.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}Fulbright Scholar alternate.

\vskip 6pt
\hangpara
{\bf 2001}\hspace{1ex}Distinguished Undergraduate Student in Linguistics, Eastern Michigan University. \textbf{One award annually}.

\vskip 6pt
\hangpara
{\bf 1999--2001}\hspace{1ex}Dean's List, Eastern Michigan University.


\vskip 20pt
\begin{flushleft}
{\bf GRANTS}
\end{flushleft}

% Add Fieldwork funding from the the university
% Add workshop funding from SAGW

\hangpara
{\bf 2019}\hspace{1ex}Swiss National Science Foundation (SNSF) Eccellenza Professorial Fellowship. Project title: `\href{http://p3.snf.ch/project-186841}{Evolution of phonetics and phonology (EVOPHON)}'. Duration 2020--2025. Steven Moran, Principal Investigator. Awarded 1,890,688 CHF (\$1,914,298). Project number PCEFP1\_186841. Description: \url{http://p3.snf.ch/project-186841}.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}`TYPDB: a unified interface to typological databases' with Balthasar Bickel, Paul Widmer and Taras Zakharko. Grant awarded from the UFSP Sprache und Raum, University of Zurich. Awarded 10,000 CHF.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}`Combining geography and language data to investigate the vertical diffusion of linguistic features due to language contact' with Curdin Deungs and Balthasar Bickel. Grant awarded from the UFSP Sprache und Raum, University of Zurich. Awarded 10,000 CHF.

\vskip 6pt
\hangpara
{\bf 2008}\hspace{1ex}PHOIBLE: Phonetics Information Base and Lexicon, with Richard Wright. Royalty Research Fund, University of Washington. Awarded \$37,375.

\vskip 6pt
\hangpara
{\bf 2007}\hspace{1ex}Student Technology Fund Proposal 2007--059--1, University of Washington Language Learning Center, Open Lab Upgrade. Awarded \$60,795.65.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}Student Technology Fund Proposal 2006--069--2, University of Washington Language Learning Center, PC Lab Replacement. Awarded \$84,829.88.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Travel grant for fieldwork in Burkina Faso, Swiss Society of Endangered Languages.

\vskip 6pt
\hangpara
{\bf 2013--2019}\hspace{1ex}Travel grants for conference travel, University of Zurich.

\vskip 6pt
\hangpara
{\bf 2006--2010}\hspace{1ex}Travel grants for conference travel, University of Washington.

\vskip 6pt
\hangpara
{\bf 2001--2005}\hspace{1ex}Travel grants for conference travel, Eastern Michigan University.


\vskip 20pt
\begin{flushleft}
{\bf ACADEMIC SERVICE: WORKSHOP ORGANIZATION}
\end{flushleft}

% \hangpara
% {\bf TBA}\hspace{1ex}`How did spoken phonology evolve in humans?' Co-sponsored by the Swiss Society for Linguistics and the Department of Comparative Linguistics, University of Zurich.

\hangpara
% \vskip 6pt
{\bf 2019}\hspace{1ex}`Current research in phonological typology', co-organized with Eitan Grossman, hosted at the 13th meeting of the Association for Linguistic Typology (ALT). September 4--6, Pavia, Italy.

\hangpara
\vskip 6pt
{\bf 2019}\hspace{1ex}`Phonological (in)stability', co-organized with Eitan Grossman, hosted at the 52nd Annual Meeting of the Societas Linguistica Europaea (SLE). August 21--24, Leipzig, Germany.

\hangpara
\vskip 6pt
{\bf 2018}\hspace{1ex}`Comparative corpus linguistics: new perspectives and applications', co-organized with Natalia Levshina and Annemarie Verkerk, hosted at the 51st Annual Meeting of the Societas Linguistica Europaea (SLE). August 29 -- September 1, Tallinn, Estonia.

\hangpara
\vskip 6pt
{\bf 2017}\hspace{1ex}`Non-linguistic causes of linguistic diversity', co-organized with Antonio Benítez Burraco and Dan Dediu, hosted at the 50th Annual Meeting of the Societas Linguistica Europaea (SLE). September 10--13, Zurich, Switzerland.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}`Multilingual Linked Open Data for Enterprises (MLODE)' co-organized with Sebastian Hellmann and co-located with Leipziger Semantic Web Day. September 24--25, Leipzig, Germany.


\vskip 20pt
\begin{flushleft}
{\bf ACADEMIC SERVICE: ADVISING}
\end{flushleft}

\hangpara
{\bf 2019--}\hspace{1ex}Elected board member of the eLinguistics Foundation (legal owner of the Linguist List and its intellectual property).

\vskip 6pt
\hangpara
{\bf 2019--}\hspace{1ex}\href{https://langsci-press.org/}{Language Science Press} Advisory Board.

\vskip 6pt
\hangpara
{\bf 2013--}\hspace{1ex}Linguist List Advisory Panel.

\vskip 6pt
\hangpara
{\bf 2007--2012}\hspace{1ex}Linguistic Society of America Technology Advisory Committee (LSA-TAC).


\vskip 20pt
\begin{flushleft}
{\bf ACADEMIC SERVICE: JOURNAL AND BOOK REVIEWING}
\end{flushleft}

\hangpara
{\bf 2021}\hspace{1ex}Reviewer for \textit{BioEssays}.

\vskip 6pt
\hangpara
{\bf 2021}\hspace{1ex}Reviewer for \textit{Language Documentation \& Conservation}.

\vskip 6pt
\hangpara
{\bf 2021}\hspace{1ex}Reviewer for \textit{Semantic Web Journal}.
% Open review: http://www.semantic-web-journal.net/content/glottocodes-identifiers-linking-families-languages-and-dialects

\hangpara
\vskip 6pt
{\bf 2021}\hspace{1ex}Reviewer for \textit{Language}.

\vskip 6pt
\hangpara
{\bf 2021}\hspace{1ex}Reviewer for \textit{Language Dynamics and Change}.

\vskip 6pt
\hangpara
{\bf 2021}\hspace{1ex}Reviewer for \textit{Linguistic Typology}.

\vskip 6pt
\hangpara
{\bf 2020--}\hspace{1ex}Editorial board member of \textit{\href{https://langsci-press.org/catalog/series/tpd}{Topics in phonological diversity}}.

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Reviewer for \textit{Diachronica}.

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Reviewer for \textit{Frontiers Psychology}.

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Reviewer for \textit{Linguistics Vanguard}.

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Reviewer for \textit{Philosophical Transactions of the Royal Society B}.

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Reviewer for \textit{Scientific Reports}.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Reviewer for \textit{Lingua}.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Reviewer for \textit{Linguistics Vanguard}.

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Reviewer for \textit{Open Handbook of Linguistic Data Management}.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Reviewer for \textit{PLOS ONE}.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Reviewer for \textit{Journal of Language Evolution}.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Reviewer for \textit{Linguistic Typology}.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Reviewer for Language Science Press.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}Reviewer for \textit{Journal of Language Evolution}.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}Reviewer for \textit{Laboratory Phonology}.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}Reviewer for \textit{Linguistic Typology}.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Reviewer for \textit{Journal of Language Evolution}.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Reviewer for \textit{Journal of the International Phonetic Association}.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Reviewer for \textit{Laboratory Phonology}.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Reviewer for \textit{Phonology}.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}Reviewer for \textit{Journal of the International Phonetic Association}.

% \vskip 6pt
% \hangpara
% {\bf 2015}\hspace{1ex}Reviewer for LRE Journal Special Issue \textit{Under-resourced Languages, Collaborative Approaches and Linked Open Data: Resources, Methods and Applications}.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}Reviewer for \textit{Language Resources and Evaluation}.

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}Reviewer for \textit{Phonology}.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Reviewer for \textit{Histoire {\'E}pist{\'e}mologie Langage}.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Reviewer for \textit{Language Resources and Evaluation}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Reviewer for \textit{Language Dynamics and Change}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Reviewer for \textit{Linked Data in Linguistics: Representing and linking lexicons, terminologies and other language data}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Reviewer for \textit{Semantic Web Journal}.

\vskip 6pt
\hangpara
{\bf 2013}\hspace{1ex}Reviewer for \textit{Studies in Language}.

\vskip 6pt
\hangpara
{\bf 2011}\hspace{1ex}Reviewer for \textit{Selected Proceedings of the 42nd Annual Conference on African Linguistics: African Languages in Context} (Michael R. Marlo, Nikki B. Adams, Christopher R. Green, Michelle Morrison and Tristan M. Purvis, eds.).


\vskip 20pt
\begin{flushleft}
{\bf ACADEMIC SERVICE: FUNDING AGENCY REVIEWING}
\end{flushleft}

\hangpara
{\bf 2019}\hspace{1ex}Reviewer for Endangered Language Documentation Programme (ELDP).

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Reviewer for Biotechnology and Biological Sciences Research Council (BBSRC).

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Reviewer for National Science Center, Poland.

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}Reviewer for Endangered Language Documentation Programme (ELDP).


\vskip 20pt
\begin{flushleft}
{\bf ACADEMIC SERVICE: CONFERENCE/WORKSHOP REVIEWING}
\end{flushleft}

% EMNLP 2021

\hangpara
{\bf 2021}\hspace{1ex}Program committee, 3rd Conference on Language, Data and Knowledge (LDK).

\hangpara
\vskip 6pt
{\bf 2021}\hspace{1ex}Reviewer for Association for Computational Linguistics and the 11th International Joint Conference on Natural Language Processing (ACL-IJCNLP).

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Reviewer for 5th Usage-Based Linguistics conference.

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Scientific committee, Evolution of Language International Conferences (EVOLANG).

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Scientific committee, 12th International Conference on Language Resources and Evaluation (LREC).

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Scientific committee, 4th Computational Methods for Endangered Languages (ComputEL-4).

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Program committee, 7th Workshop on Linked Data in Linguistics (LDL)

\vskip 6pt
\hangpara
{\bf 2020}\hspace{1ex}Program committee, 28th International Conference on Computational Linguistics (COLING)

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Scientific committee, 2nd Conference on Language, Data, and Knowledge (LDK).

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Program committee, Association Linguistic Typology (ALT 13).

\vskip 6pt
\hangpara
{\bf 2019}\hspace{1ex}Program committee, Language, Data and Knowledge (LDK).

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Program committee, 6th Workshop on Linked Data in Linguistics (LDL): Towards Linguistic Data Science.

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Program committee, Conference on Computational Linguistics (COLING).

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Program committee, International Conference for Graduate students on Diverse Approaches to Linguistics (IGDAL 7).

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Scientific committee, 3rd Computational Methods for Endangered Languages (ComputEL-3).

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Scientific committee, 11th International Conference on Language Resources and Evaluation Conference (LREC).

\vskip 6pt
\hangpara
{\bf 2018}\hspace{1ex}Scientific committee, Evolution of Language International Conferences (EVOLANG).

\vskip 6pt
\hangpara
{\bf 2017}\hspace{1ex}Program committee, 1st International Conference on Language, Data and Knowledge (LDK).

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Scientific committee, 10th International Conference on Language Resources and Evaluation (LREC).

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Scientific committee, 2nd Workshop on Computational Methods for Endangered Languages (ComputEL-2).

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Program committee, 2nd Workshop on Collaboration and Computing for Under-Resourced Languages (CCURL): Towards an Alliance for Digital Language Diversity.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Program committee, 5th Workshop on Linked Data in Linguistics (LDL): Managing, Building and Using Linked Language Resources.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Program committee, Terminology and Knowledge Engineering (TKE): Term Bases and Linguistic Linked Open Data.

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Program committee, First Workshop on Knowledge Extraction and Knowledge Integration (KEKI).

\vskip 6pt
\hangpara
{\bf 2016}\hspace{1ex}Program committee, International Conference on Computational Linguistics (COLING).

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}Scientific committee, Association for Linguistic Typology (ALT 11).

\vskip 6pt
\hangpara
{\bf 2015}\hspace{1ex}Program committee, 4th Workshop on Linked Data in Linguistics (LDL): Resources and Applications.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Program committee, Collaboration and Computing for Under-resourced Languages in the Linked Open Data Era (CCURL).

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Program committee, 3rd Workshop on Linked Data in Linguistics (LDL): Multilingual Knowledge Resources and Natural Language Processing.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Scientific committee, 8th Days of Swiss Linguistics.

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Scientific committee, 9th International Conference on Language Resources and Evaluation (LREC).

\vskip 6pt
\hangpara
{\bf 2014}\hspace{1ex}Scientific committee, 1st Workshop on Computational Methods for Endangered Languages (ComputEL).

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}Program committee, Deutsche Gesellschaft f{\"u}r Sprachwissenschaft (DGfS) Workshop: Linked Data in Linguistics.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}Program committee, European Association of Computational Linguistics (EACL) Workshop: LINGVIS \& UNCLH.

\vskip 6pt
\hangpara
{\bf 2012}\hspace{1ex}Program committee, Proceedings of Annual Conference on African Linguistics.


\vskip 20pt
\begin{flushleft}
{\bf ACADEMIC SERVICE: OTHER}
\end{flushleft}

\hangpara
{\bf 2006}\hspace{1ex}Technical liaison for the 25th West Coast Conference on Formal Linguistics. April 28--30. University of Washington, Seattle, Washington.

\vskip 6pt
\hangpara
{\bf 2006}\hspace{1ex}Media coordinator for Word Languages Day 2006. March 3. University of Washington, Seattle, Washington.	

\vskip 6pt
\hangpara
{\bf 2005--2009}\hspace{1ex}Editor of the \textit{University of Washington Working Papers in Linguistics}.

\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}Liaison and media coordinator at the Breath of Life Conference at the University of Washington. September 12--16, Seattle, Washington.

\vskip 6pt
\hangpara
{\bf 2005}\hspace{1ex}Working group liaison at the E-MELD Workshop 2005: Conference on Linguistic Ontologies and Data Categories for Language Resources. July 1--3, Cambridge, Massachusetts.

\vskip 6pt
\hangpara
{\bf 2004}\hspace{1ex}Working group liaison for the E-MELD Workshop 2004: Conference on Linguistic Databases and Best Practice. July 15--18, Detroit, Michigan.

\vskip 6pt
\hangpara
{\bf 2003}\hspace{1ex}Voluntary instructor of English Grammar and Conversation. Lambussie Secondary School. Lambussie, Ghana.

\vskip 6pt
\hangpara
{\bf 2002}\hspace{1ex}Working group liaison for the E-MELD Workshop 2002: Conference on Digitizing Lexical Information. August 2--5, Ypsilanti, Michigan.



\vskip 20pt
\begin{flushleft}
{\bf PROFESSIONAL MEMBERSHIPS (PAST \& PRESENT)}
\end{flushleft}
\begin{itemize}
\item American Association for the Advancement of Science (AAAS)
\item Association of Computational Linguistics (ACL)
\item Association of Linguistic Typology (ALT)
\item Center for the Interdisciplinary Study of Language Evolution (ISLE)
\item European Language Resources Association (ELRA)
\item Linguistic Society of America (LSA)
\item Linguistics Society at the University of Washington (LSUW)
\item Open Working Group in Linguistics (OWLG)
\item Schweizerische Gesellschaft f{\"u}r bedrohte Sprachen (SGBS)
\item Societas Linguistica Europaea (SLE)
\item Z{\"u}richer Kompetenzzentrum Linguistik (Z{\"u}KL)
\end{itemize}

\vskip 20pt
\today

\end{document}
